Component response rate variation underlies the stability of complex systems

### 2020-03-11 notebook/ms.Rmd
Add another paragraph on the relationship between rho and the stability

Numerical simulations reveal that $\sigma^{2}_{\gamma} > 0$ results in a nonlinear relationship between $\rho$ and $\max(\Re(\lambda))$, which can sometimes increase the stability of the system.

>>>>

Ten thousand numerical simulations of $\mathbf{M}$ revealed that $\sigma^{2}_{\gamma} > 0$ results in a nonlinear relationship between $\rho$ and $\max(\Re(\lambda))$, which can sometimes increase the stability of the system. Figure 2 shows a comparison of $\max(\Re(\lambda))$ across $\rho$ values when $\sigma^{2}_{\gamma} = 0$ versus $\sigma^{2}_{\gamma} = 1/3$. For $-0.4 \leq \rho \leq 0.7$ (shaded region of Figure 2), expected $\max(\Re(\lambda))$ was lower given $\sigma^{2}_{\gamma} = 1/3$. For $\rho \geq -0.1$, the range of $\max(\Re(\lambda))$ values observed given $\sigma^{2}_{\gamma} = 1/3$ also had a lower bound, which included negative values for $\rho = -0.1$ and $\rho = 0$. Hence, across a wide range of system correlations, variation in the response rate of system components had a stabilising effect.

The stabilising effect of $\sigma^{2}_{\gamma}$ across $\rho$ increases with increasing $S$. Figure 3 shows 10000 numerical simulations of $\mathbf{M}$ for $\sigma^{2}_{\gamma} = 0$ versus $\sigma^{2}_{\gamma} = 1/3$ across increasing $S$.

### 2020-03-11 notebook/ms.tex
Add another paragraph on the relationship between rho and the stability

\hypertarget{abstract}{%
\subsection{Abstract}\label{abstract}}

@@

\hypertarget{introduction}{%
\subsection{Introduction}\label{introduction}}

@@

\hypertarget{results}{%
\subsection{Results}\label{results}}

@@

If \(\rho < 0\), such as when \(\textbf{M}\) models a predator-prey
system in which \(M_{ij}\) and \(M_{ji}\) have opposing signs, stability
increases\textsuperscript{\protect\hyperlink{ref-Allesina2012}{2}}. If
diagonal elements of \(\gamma\) vary independently, the magnitude of
\(\rho\) is decreased because \(\sigma^{2}_{\gamma}\) increases the
variance of \(M_{ij}\) without affecting the expected covariance between
\(M_{ij}\) and \(M_{ji}\),

\begin{equation} \label{rho_def}
\rho = \frac{cov(M_{ij}, M_{ji})}{\sigma^{2}_{A}(1 + \sigma^{2}_{\gamma})}.
\end{equation}

Neverthless, numerical simulations reveal that
\(\sigma^{2}_{\gamma} > 0\) results in a nonlinear relationship between
\(\rho\) and \(\max(\Re(\lambda))\), which can sometimes increase the
stability of the system.

\textbf{Numerical simulations of random \(\mathbf{M}\) with and without
\(\mathbf{\sigma_{\gamma}}\)}. I used numerical simulations to isolate
the effect of \(\sigma_{\gamma}\) on system stability by comparing the
same \(\textbf{M} = \gamma \textbf{A}\) given \(\sigma_{\gamma} > 0\)
versus \(\sigma_{\gamma} = 0\) across a rane of parameter combinations.
Values of \(\gamma_{ii}\) were sampled from a uniform distribution where
\(\gamma \sim \mathcal{U}(0, 2)\) (see Supplementary Information for
other distributions, which give similar results). For
\(\sigma_{\gamma} = 0\), diagonal elements were standardised to the mean
value of sampled \(\gamma_{ii}\) so that \(E[d]\) of \(\textbf{M}\) were
identical.

@@

@@

\hypertarget{discussion}{%
\subsection{Discussion}\label{discussion}}

@@

\hypertarget{methods}{%
\subsection{Methods}\label{methods}}

\textbf{Component response rate variation (\(\mathbf{\gamma}\))}. In a
synthesis of eco-evolutionary feedbacks on community stability, Patel et
al.~model a system that includes a vector of potentially changing
species densities (\(\mathbf{N}\)) and a vector of potentially evolving
traits
(\(\mathbf{x}\))\textsuperscript{\protect\hyperlink{ref-Patel2018}{18}}.
For any species \(i\) or trait \(j\), change in species density
(\(N_{i}\)) or trait value (\(x_{j}\)) with time (\(t\)) is a function
of the vectors \(\mathbf{N}\) and \(\mathbf{x}\),

@@

In the above, \(f_{i}\) and \(g_{j}\) are functions that define the
effects of all species densities and trait values on the density of a
species \(i\) and the value of trait \(j\), respectively. Patel et
al.~were interested in stability when the evolution of traits was
relatively slow or fast in comparison with the change in species
densities\textsuperscript{\protect\hyperlink{ref-Patel2018}{18}}, and
this is modulated in the above by the scalar \(\epsilon\). The value of
\(\epsilon\) thereby determines the timescale separation between ecology
and evolution, with high \(\epsilon\) modelling relatively fast
evolution and low \(\epsilon\) modelling relative slow
evolution\textsuperscript{\protect\hyperlink{ref-Patel2018}{18}}.

I use the same principle that Patel et al.~use to modulate the relative
rate of evolution to modulate rates of component responses for \(S\)
components. Following
May\textsuperscript{\protect\hyperlink{ref-May1972}{1},\protect\hyperlink{ref-May1973}{28}},
the value of a component \(i\) at time \(t\) (\(v_{i}(t)\)) is affected
by the value of \(j\) (\(v_{j}(t)\)) and \(j\)'s marginal effect on
\(i\) (\(a_{ij}\)), and by \(i\)'s response rate (\(\gamma_{i}\)),

@@

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-May1972}{}%
1. May, R. M. Will a large complex system be stable? \emph{Nature}
\textbf{238,} 413--414 (1972).

\leavevmode\hypertarget{ref-Allesina2012}{}%
2. Allesina, S. \& Tang, S. Stability criteria for complex ecosystems.
\emph{Nature} \textbf{483,} 205--208 (2012).

\leavevmode\hypertarget{ref-Mougi2012}{}%
3. Mougi, A. \& Kondoh, M. Diversity of interaction types and ecological
community stability. \emph{Science} \textbf{337,} 349--351 (2012).

\leavevmode\hypertarget{ref-Allesina2015}{}%
4. Allesina, S. \emph{et al.} Predicting the stability of large
structured food webs. \emph{Nature Communications} \textbf{6,} 7842
(2015).

\leavevmode\hypertarget{ref-Grilli2017}{}%
5. Grilli, J. \emph{et al.} Feasibility and coexistence of large
ecological communities. \emph{Nature Communications} \textbf{8,} (2017).

\leavevmode\hypertarget{ref-Gray2008}{}%
6. Gray, R. T. \& Robinson, P. A. Stability and synchronization of
random brain networks with a distribution of connection strengths.
\emph{Neurocomputing} \textbf{71,} 1373--1387 (2008).

\leavevmode\hypertarget{ref-Gray2009}{}%
7. Gray, R. T. \& Robinson, P. A. Stability of random brain networks
with excitatory and inhibitory connections. \emph{Neurocomputing}
\textbf{72,} 1849--1858 (2009).

\leavevmode\hypertarget{ref-Rosenfeld2009}{}%
8. Rosenfeld, S. Patterns of stochastic behavior in dynamically unstable
high-dimensional biochemical networks. \emph{Gene Regulation and Systems
Biology} \textbf{3,} 1--10 (2009).

\leavevmode\hypertarget{ref-MacArthur2010}{}%
9. MacArthur, B. D., Sanchez-Garcia, R. J. \& Ma'ayan, A. Microdynamics
and criticality of adaptive regulatory networks. \emph{Physics Review
Letters} \textbf{104,} 168701 (2010).

\leavevmode\hypertarget{ref-May2008}{}%
10. May, R. M., Levin, S. A. \& Sugihara, G. Complex systems: Ecology
for bankers. \emph{Nature} \textbf{451,} 893--895 (2008).

\leavevmode\hypertarget{ref-Haldane2011}{}%
11. Haldane, A. G. \& May, R. M. Systemic risk in banking ecosystems.
\emph{Nature} \textbf{469,} 351--355 (2011).

\leavevmode\hypertarget{ref-Suweis2014}{}%
12. Suweis, S. \& D'Odorico, P. Early warning signs in social-ecological
networks. \emph{PLoS ONE} \textbf{9,} (2014).

\leavevmode\hypertarget{ref-Bardoscia2017}{}%
13. Bardoscia, M., Battiston, S., Caccioli, F. \& Caldarelli, G.
Pathways towards instability in financial networks. \emph{Nature
Communications} \textbf{8,} 1--7 (2017).

\leavevmode\hypertarget{ref-Tao2010}{}%
14. Tao, T. \& Vu, V. Random matrices: Universality of ESDs and the
circular law. \emph{Annals of Probability} \textbf{38,} 2023--2065
(2010).

\leavevmode\hypertarget{ref-Watts1998}{}%
15. Watts, D. J. \& Strogatz, S. H. Collective dynamics of 'small world'
networks. \emph{Nature} \textbf{393,} 440--442 (1998).

\leavevmode\hypertarget{ref-Albert2002}{}%
16. Albert, R. \& Barabási, A. L. Statistical mechanics of complex
networks. \emph{Reviews of Modern Physics} \textbf{74,} 47--97 (2002).

\leavevmode\hypertarget{ref-Williams2000}{}%
17. Williams, R. J. \& Martinez, N. D. Simple rules yield complex food
webs. \emph{Nature} \textbf{404,} 180--183 (2000).

\leavevmode\hypertarget{ref-Patel2018}{}%
18. Patel, S., Cortez, M. H. \& Schreiber, S. J. Partitioning the
effects of eco-evolutionary feedbacks on community stability.
\emph{American Naturalist} \textbf{191,} 1--29 (2018).

\leavevmode\hypertarget{ref-Tang2014b}{}%
19. Tang, S. \& Allesina, S. Reactivity and stability of large
ecosystems. \emph{Frontiers in Ecology and Evolution} \textbf{2,} 1--8
(2014).

\leavevmode\hypertarget{ref-Ahmadian2015}{}%
20. Ahmadian, Y., Fumarola, F. \& Miller, K. D. Properties of networks
with partially structured and partially random connectivity.
\emph{Physical Review E - Statistical, Nonlinear, and Soft Matter
Physics} \textbf{91,} 012820 (2015).

\leavevmode\hypertarget{ref-Gibbs2017}{}%
21. Gibbs, T., Grilli, J., Rogers, T. \& Allesina, S. The effect of
population abundances on the stability of large random ecosystems.
\emph{Physical Review E - Statistical, Nonlinear, and Soft Matter
Physics} \textbf{98,} 022410 (2018).

\leavevmode\hypertarget{ref-Stone2017}{}%
22. Stone, L. The feasibility and stability of large complex biological
networks: a random matrix approach. \emph{Scientific Reports}
\textbf{8,} 8246 (2018).

\leavevmode\hypertarget{ref-Tang2014c}{}%
23. Tang, S., Pawar, S. \& Allesina, S. Correlation between interaction
strengths drives stability in large ecological networks. \textbf{17,}
1094--1100 (2014).

\leavevmode\hypertarget{ref-Hamblin2013}{}%
24. Hamblin, S. On the practical usage of genetic algorithms in ecology
and evolution. \emph{Methods in Ecology and Evolution} \textbf{4,}
184--194 (2013).

\leavevmode\hypertarget{ref-Dougoud2018}{}%
25. Dougoud, M., Vinckenbosch, L., Rohr, R., Bersier, L.-F. \& Mazza, C.
The feasibility of equilibria in large ecosystems: a primary but
neglected concept in the complexity-stability debate. \emph{PLOS
Computational Biology} \textbf{14,} e1005988 (2018).

\leavevmode\hypertarget{ref-Song2018}{}%
26. Song, C. \& Saavedra, S. Will a small randomly assembled community
be feasible and stable? \emph{Ecology} \textbf{99,} 743--751 (2018).

\leavevmode\hypertarget{ref-Servan2018}{}%
27. Serván, C. A., Capitán, J. A., Grilli, J., Morrison, K. E. \&
Allesina, S. Coexistence of many species in random ecosystems.
\emph{Nature Ecology and Evolution} \textbf{2,} 1237--1242 (2018).

\leavevmode\hypertarget{ref-May1973}{}%
28. May, R. M. Qualitative stability in model ecosystems. \emph{Ecology}
\textbf{54,} 638--641 (1973).

@@

\textbf{Figure 1: Eigenvalue distributions of random complex systems.}
Each panel shows the real (x-axis) and imaginary (y-axis) parts of
\(S =\) 400 eigenvalues from random \(S \times S\) matrices.
(\(\textbf{a}\)) A system represented by a matrix \(\mathbf{A}\), in
which all elements are sampled from a normal distribution with
\(\mu = 0\) and \(\sigma_{A} = 1/\sqrt{S}\). Points are uniformly
distributed within a circle centred at the origin with a radius of
\(\sigma_{A} \sqrt{S} = 1\). (\(\textbf{b}\)) The same system after
including variation in the response rates of \(S\) components,
represented by the diagonal matrix \(\gamma\), such that
\(\mathbf{M} = \gamma\mathbf{A}\). Elements of \(\gamma\) are randomly
sampled from a uniform distribution from \(\min = 0\) to \(\max = 2\).
Eigenvalues of \(\mathbf{M}\) are then distributed non-uniformly within
a circle centred at the origin with a radius of
\(\sqrt{\sigma^{2}_{A}(1 + \sigma^{2}_{\gamma})S} \approx\) 1.16.
(\(\textbf{c}\)) A different random system \(\mathbf{A}\) constructed
from the same parameters as in \(\textbf{a}\), except with diagonal
values of \(-1\). (\(\textbf{d}\)) The same system \(\textbf{c}\) after
including variation in component response rates, sampled from
\(\mathcal{U}(0, 2)\) as in \(\textbf{b}\).

>>>>

\subsection{Abstract}\label{abstract}

@@

\subsection{Introduction}\label{introduction}

@@

\subsection{Results}\label{results}

@@

If \(\rho < 0\), such as when \(\textbf{M}\) models a predator-prey
system in which \(M_{ij}\) and \(M_{ji}\) have opposing signs, stability
increases\textsuperscript{\protect\hyperlink{ref-Allesina2012}{2}}. If
diagonal elements of \(\gamma\) vary independently, the magnitude of
\(\rho\) is decreased because \(\sigma^{2}_{\gamma}\) increases the
variance of \(M_{ij}\) without affecting the expected covariance between
\(M_{ij}\) and \(M_{ji}\).

\textbf{Numerical simulations of random \(\mathbf{M}\) with and without
\(\mathbf{\sigma^{2}_{\gamma}}\)}. I used numerical simulations and
eigenanalysis to test how variation in \(\gamma\) affects stability in
random matrices with known properties, comparing the stability of
\(\textbf{A}\) versus \(\mathbf{M} = \gamma\mathbf{A}\). Values of
\(\gamma\) were sampled from a uniform distribution where
\(\gamma_{i} \sim \mathcal{U}(0, 2)\) and \(\sigma^{2}_{\gamma} = 1/3\)
(see Supplementary Information for other distributions, which give
similar results). Diagonal elements of simulated \(\mathbf{A}\) were
standardised to the mean value of sampled \(\gamma\) so that \(E[d]\) of
\(\textbf{M}\) and \(\textbf{M}\) were guaranteed to be identical. Here
I focus on the effect of \(\gamma\) across values of \(\rho\), and for
increasing system sizes (\(S\)) in random and structured networks. By
increasing \(S\), the objective is to determine the effect of \(\gamma\)
as system complexity increases toward the boundary at which stability is
realistic for a finite system.

@@

Numerical simulations reveal that \(\sigma^{2}_{\gamma} > 0\) results in
a nonlinear relationship between \(\rho\) and \(\max(\Re(\lambda))\),
which can sometimes increase the stability of the system.

@@

\subsection{Discussion}\label{discussion}

@@

\subsection{Methods}\label{methods}

\textbf{Component response rate variation (\(\mathbf{\gamma}\))}. In a
synthesis of eco-evolutionary feedbacks on community stability, Patel et
al. model a system that includes a vector of potentially changing
species densities (\(\mathbf{N}\)) and a vector of potentially evolving
traits
(\(\mathbf{x}\))\textsuperscript{\protect\hyperlink{ref-Patel2018}{18}}.
For any species \(i\) or trait \(j\), change in species density
(\(N_{i}\)) or trait value (\(x_{j}\)) with time (\(t\)) is a function
of the vectors \(\mathbf{N}\) and \(\mathbf{x}\),

@@

In the above, \(f_{i}\) and \(g_{j}\) are functions that define the
effects of all species densities and trait values on the density of a
species \(i\) and the value of trait \(j\), respectively. Patel et al.
were interested in stability when the evolution of traits was relatively
slow or fast in comparison with the change in species
densities\textsuperscript{\protect\hyperlink{ref-Patel2018}{18}}, and
this is modulated in the above by the scalar \(\epsilon\). The value of
\(\epsilon\) thereby determines the timescale separation between ecology
and evolution, with high \(\epsilon\) modelling relatively fast
evolution and low \(\epsilon\) modelling relative slow
evolution\textsuperscript{\protect\hyperlink{ref-Patel2018}{18}}.

I use the same principle that Patel et al. use to modulate the relative
rate of evolution to modulate rates of component responses for \(S\)
components. Following
May\textsuperscript{\protect\hyperlink{ref-May1972}{1},\protect\hyperlink{ref-May1973}{28}},
the value of a component \(i\) at time \(t\) (\(v_{i}(t)\)) is affected
by the value of \(j\) (\(v_{j}(t)\)) and \(j\)'s marginal effect on
\(i\) (\(a_{ij}\)), and by \(i\)'s response rate (\(\gamma_{i}\)),

@@

\hypertarget{refs}{}
\hypertarget{ref-May1972}{}
1. May, R. M. Will a large complex system be stable? \emph{Nature}
\textbf{238,} 413--414 (1972).

\hypertarget{ref-Allesina2012}{}
2. Allesina, S. \& Tang, S. Stability criteria for complex ecosystems.
\emph{Nature} \textbf{483,} 205--208 (2012).

\hypertarget{ref-Mougi2012}{}
3. Mougi, A. \& Kondoh, M. Diversity of interaction types and ecological
community stability. \emph{Science} \textbf{337,} 349--351 (2012).

\hypertarget{ref-Allesina2015}{}
4. Allesina, S. \emph{et al.} Predicting the stability of large
structured food webs. \emph{Nature Communications} \textbf{6,} 7842
(2015).

\hypertarget{ref-Grilli2017}{}
5. Grilli, J. \emph{et al.} Feasibility and coexistence of large
ecological communities. \emph{Nature Communications} \textbf{8,} (2017).

\hypertarget{ref-Gray2008}{}
6. Gray, R. T. \& Robinson, P. A. Stability and synchronization of
random brain networks with a distribution of connection strengths.
\emph{Neurocomputing} \textbf{71,} 1373--1387 (2008).

\hypertarget{ref-Gray2009}{}
7. Gray, R. T. \& Robinson, P. A. Stability of random brain networks
with excitatory and inhibitory connections. \emph{Neurocomputing}
\textbf{72,} 1849--1858 (2009).

\hypertarget{ref-Rosenfeld2009}{}
8. Rosenfeld, S. Patterns of stochastic behavior in dynamically unstable
high-dimensional biochemical networks. \emph{Gene Regulation and Systems
Biology} \textbf{3,} 1--10 (2009).

\hypertarget{ref-MacArthur2010}{}
9. MacArthur, B. D., Sanchez-Garcia, R. J. \& Ma'ayan, A. Microdynamics
and criticality of adaptive regulatory networks. \emph{Physics Review
Letters} \textbf{104,} 168701 (2010).

\hypertarget{ref-May2008}{}
10. May, R. M., Levin, S. A. \& Sugihara, G. Complex systems: Ecology
for bankers. \emph{Nature} \textbf{451,} 893--895 (2008).

\hypertarget{ref-Haldane2011}{}
11. Haldane, A. G. \& May, R. M. Systemic risk in banking ecosystems.
\emph{Nature} \textbf{469,} 351--355 (2011).

\hypertarget{ref-Suweis2014}{}
12. Suweis, S. \& D'Odorico, P. Early warning signs in social-ecological
networks. \emph{PLoS ONE} \textbf{9,} (2014).

\hypertarget{ref-Bardoscia2017}{}
13. Bardoscia, M., Battiston, S., Caccioli, F. \& Caldarelli, G.
Pathways towards instability in financial networks. \emph{Nature
Communications} \textbf{8,} 1--7 (2017).

\hypertarget{ref-Tao2010}{}
14. Tao, T. \& Vu, V. Random matrices: Universality of ESDs and the
circular law. \emph{Annals of Probability} \textbf{38,} 2023--2065
(2010).

\hypertarget{ref-Watts1998}{}
15. Watts, D. J. \& Strogatz, S. H. Collective dynamics of 'small world'
networks. \emph{Nature} \textbf{393,} 440--442 (1998).

\hypertarget{ref-Albert2002}{}
16. Albert, R. \& Barabási, A. L. Statistical mechanics of complex
networks. \emph{Reviews of Modern Physics} \textbf{74,} 47--97 (2002).

\hypertarget{ref-Williams2000}{}
17. Williams, R. J. \& Martinez, N. D. Simple rules yield complex food
webs. \emph{Nature} \textbf{404,} 180--183 (2000).

\hypertarget{ref-Patel2018}{}
18. Patel, S., Cortez, M. H. \& Schreiber, S. J. Partitioning the
effects of eco-evolutionary feedbacks on community stability.
\emph{American Naturalist} \textbf{191,} 1--29 (2018).

\hypertarget{ref-Tang2014b}{}
19. Tang, S. \& Allesina, S. Reactivity and stability of large
ecosystems. \emph{Frontiers in Ecology and Evolution} \textbf{2,} 1--8
(2014).

\hypertarget{ref-Ahmadian2015}{}
20. Ahmadian, Y., Fumarola, F. \& Miller, K. D. Properties of networks
with partially structured and partially random connectivity.
\emph{Physical Review E - Statistical, Nonlinear, and Soft Matter
Physics} \textbf{91,} 012820 (2015).

\hypertarget{ref-Gibbs2017}{}
21. Gibbs, T., Grilli, J., Rogers, T. \& Allesina, S. The effect of
population abundances on the stability of large random ecosystems.
\emph{Physical Review E - Statistical, Nonlinear, and Soft Matter
Physics} \textbf{98,} 022410 (2018).

\hypertarget{ref-Stone2017}{}
22. Stone, L. The feasibility and stability of large complex biological
networks: a random matrix approach. \emph{Scientific Reports}
\textbf{8,} 8246 (2018).

\hypertarget{ref-Tang2014c}{}
23. Tang, S., Pawar, S. \& Allesina, S. Correlation between interaction
strengths drives stability in large ecological networks. \textbf{17,}
1094--1100 (2014).

\hypertarget{ref-Hamblin2013}{}
24. Hamblin, S. On the practical usage of genetic algorithms in ecology
and evolution. \emph{Methods in Ecology and Evolution} \textbf{4,}
184--194 (2013).

\hypertarget{ref-Dougoud2018}{}
25. Dougoud, M., Vinckenbosch, L., Rohr, R., Bersier, L.-F. \& Mazza, C.
The feasibility of equilibria in large ecosystems: a primary but
neglected concept in the complexity-stability debate. \emph{PLOS
Computational Biology} \textbf{14,} e1005988 (2018).

\hypertarget{ref-Song2018}{}
26. Song, C. \& Saavedra, S. Will a small randomly assembled community
be feasible and stable? \emph{Ecology} \textbf{99,} 743--751 (2018).

\hypertarget{ref-Servan2018}{}
27. Serván, C. A., Capitán, J. A., Grilli, J., Morrison, K. E. \&
Allesina, S. Coexistence of many species in random ecosystems.
\emph{Nature Ecology and Evolution} \textbf{2,} 1237--1242 (2018).

\hypertarget{ref-May1973}{}
28. May, R. M. Qualitative stability in model ecosystems. \emph{Ecology}
\textbf{54,} 638--641 (1973).

@@

\textbf{Figure 1: Eigenvalue distributions of random complex systems.}
Each panel shows the real (x-axis) and imaginary (y-axis) parts of
\(S =\) 400 eigenvalues from random \(S \times S\) matrices.
(\(\textbf{a}\)) A system represented by a matrix \(\mathbf{A}\), in
which all elements are sampled from a normal distribution with
\(\mu = 0\) and \(\sigma_{A} = 1/\sqrt{S}\). Points are uniformly
distributed within a circle centred at the origin with a radius of
\(\sigma_{A} \sqrt{S} = 1\). (\(\textbf{b}\)) The same system after
including variation in the response rates of \(S\) components,
represented by the diagonal matrix \(\gamma\), such that
\(\mathbf{M} = \gamma\mathbf{A}\). Elements of \(\gamma\) are randomly
sampled from a uniform distribution from \(\min = 0\) to \(\max = 2\).
Eigenvalues of \(\mathbf{M}\) are then distributed non-uniformly within
a circle centred at the origin with a radius of
\(\sqrt{\sigma^{2}_{A}(1 + \sigma^{2}_{\gamma})S} \approx\) 1.14.
(\(\textbf{c}\)) A different random system \(\mathbf{A}\) constructed
from the same parameters as in \(\textbf{a}\), except with diagonal
values of \(-1\). (\(\textbf{d}\)) The same system \(\textbf{c}\) after
including variation in component response rates, sampled from
\(\mathcal{U}(0, 2)\) as in \(\textbf{b}\).
